Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-11 writeup/parkinsons.tex
add extra cluster estimation methods

\documentclass[letter,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{tablefootnote}
\pagestyle{fancy}
\lhead{Jesse Mu}
\rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|l|l|l}
    Name & Type & Format & Description \\
    \hline
    nms\_d1 & byte & \%8.0g & cardiovascular \\
    nms\_d2 & byte & \%8.0g & sleep/fatigue \\
    nms\_d3 & byte & \%8.0g & mood/cognition \\
    nms\_d4 & byte & \%8.0g & percep/hallucinations \\
    nms\_d5 & byte & \%8.0g & attention/memory \\
    nms\_d6 & byte & \%8.0g & gastrointestinal \\
    nms\_d7 & byte & \%8.0g & urinary \\
    nms\_d8 & byte & \%8.0g & sexual function \\
    nms\_d9 & byte & \%8.0g & miscellaneous \\
    tremor & float & \%9.0g & tremor \\
    bradykin & float & \%9.0g & bradykinesia\tablefootnote{Impaired ability to
    adjust the body's position.} \\
    rigidity & float & \%9.0g & rigidity \\
    axial & float & \%9.0g & axial\tablefootnote{Issues affecting the middle of
    the body.} \\
    pigd & float & \%9.0g & postural instability and gait difficulty \\
  \end{tabular}
  \caption{Selected Features and Details}
  \label{tab:selcted_features}
\end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{l|l|l|l}
  Name  &       $\mu$ & $\sigma$ & min-max \\
         \hline
nms\_d1&   1.76&  3.32&   0-24 \\
nms\_d2&   8.71&  8.76&   0-48 \\
nms\_d3&   8.70& 11.83&   0-60 \\
nms\_d4&   1.65&  3.94&   0-33 \\
nms\_d5&   5.22&  7.44&   0-36 \\
nms\_d6&   5.67&  6.92&   0-36 \\
nms\_d7&   8.02&  9.09&   0-36 \\
nms\_d8&   3.57&  5.97&   0-24 \\
nms\_d9&   6.99&  7.74&   0-48 \\
tremor&   2.59&  2.63&   0-12 \\
bradykin& 2.49&  1.39&   0-6 \\
rigidity& 2.34&  1.36&   0-6 \\
axial&    3.28&  2.75&   0-12 \\
pigd&     3.36&  2.77&   0-12 \\
  \end{tabular}
  \caption{Descriptive Statistics}
  \label{tab:descriptive_statistics}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{pca-eigenvalues.png}
  \caption{Scree test: eigenvalues by factor}
  \label{fig:pca-eigenvalues}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-wss-error.png}
  \caption{Scree test: WSS error by cluster size}
  \label{fig:kmeans-wss-error}
\end{figure}

@@

% TODO: More optimal cluster determination (PAMK, NbClust)

@@

% Pruned, non-pruned tree

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{tablefootnote}
% \pagestyle{fancy}
% \lhead{Jesse Mu}
% \rhead{CSCI339 Term Project}
\graphicspath{ {../figures/} }

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l}
    Name & Type & Format & Description \\
    \hline
    nms\_d1 & byte & \%8.0g & cardiovascular \\
    nms\_d2 & byte & \%8.0g & sleep/fatigue \\
    nms\_d3 & byte & \%8.0g & mood/cognition \\
    nms\_d4 & byte & \%8.0g & percep/hallucinations \\
    nms\_d5 & byte & \%8.0g & attention/memory \\
    nms\_d6 & byte & \%8.0g & gastrointestinal \\
    nms\_d7 & byte & \%8.0g & urinary \\
    nms\_d8 & byte & \%8.0g & sexual function \\
    nms\_d9 & byte & \%8.0g & miscellaneous \\
    tremor & float & \%9.0g & tremor \\
    bradykin & float & \%9.0g & bradykinesia\tablefootnote{Impaired ability to
    adjust the body's position.} \\
    rigidity & float & \%9.0g & rigidity \\
    axial & float & \%9.0g & axial\tablefootnote{Issues affecting the middle of
    the body.} \\
    pigd & float & \%9.0g & postural instability and gait difficulty \\
  \end{tabular}
  \caption{Selected Features and Details}
  \label{tab:selcted_features}
\end{table}

\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l}
  Name  &       $\mu$ & $\sigma$ & min-max \\
         \hline
nms\_d1&   1.76&  3.32&   0-24 \\
nms\_d2&   8.71&  8.76&   0-48 \\
nms\_d3&   8.70& 11.83&   0-60 \\
nms\_d4&   1.65&  3.94&   0-33 \\
nms\_d5&   5.22&  7.44&   0-36 \\
nms\_d6&   5.67&  6.92&   0-36 \\
nms\_d7&   8.02&  9.09&   0-36 \\
nms\_d8&   3.57&  5.97&   0-24 \\
nms\_d9&   6.99&  7.74&   0-48 \\
tremor&   2.59&  2.63&   0-12 \\
bradykin& 2.49&  1.39&   0-6 \\
rigidity& 2.34&  1.36&   0-6 \\
axial&    3.28&  2.75&   0-12 \\
pigd&     3.36&  2.77&   0-12 \\
  \end{tabular}
  \caption{Descriptive Statistics}
  \label{tab:descriptive_statistics}
\end{table}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{pca-eigenvalues.png}
  \caption{Scree test: eigenvalues by factor}
  \label{fig:pca-eigenvalues}
\end{figure}

@@

\subsubsection{WSS Error Scree Test}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-wss-error.png}
  \caption{Scree test: WSS error by cluster size}
  \label{fig:kmeans-wss-error}
\end{figure}

@@

\subsubsection{Gap Statistic}

Optimal cluster is the local maximum of the gap statistic, but it appears to be
consistently increasing in Figure~\ref{fig:gap-statistic}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{gap-statistic.png}
  \caption{Gap statistic by cluster size}
  \label{fig:gap-statistic}
\end{figure}

\subsubsection{Average Silhouette Width}

Figure~\ref{fig:asw} shows average silhouette width as being consistently under
0.25 for all clusters, implying the data is not well structured.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{asw.png}
  \caption{Average silhouette width by cluster size}
  \label{fig:asw}
\end{figure}

% \subsubsection{\texttt{NbClust} package}

@@

% TODO: Use compressed function to plot decision trees based on clusters with
% 2, 3, 4 groups.
% See if there are any common factors here!
